Formalization of Forcing in Isabelle/ZF \thanks{Supported by Secyt-UNC project 33620180100465CB and Conicet.}

### 2020-01-21 IJCAR2020/intro.tex

\begin{framed}
  We implemented an automatic ML machinery of (bounded) renaming
  of formulas.
\end{framed}

>>>>

In the course of our work we find it useful to develop Isar methods to
automate repetitive tasks. Part of the interface with Paulson's
library consisted in constructing formulas for each relativized
concept; Isar already has a method (\texttt{schematic\_goal}) which can
synthesize terms for unbound schematic variables in theorems. The
synthesized term, however, is not available outside the theorem; we
introduced a method that creates a definition from a schematic
goal. The second method is concerned with renaming of formulas: we
improved our small library of bounded renamings with a method that
given the source and target environments figures out the renaming
function and produces the relevant lemmas about it.

\begin{framed}
  TODO: Comentar en algún lado las limitaciones del método de
  definiciones sintetizadas.

  TODO: Explicar mejor que las fórmulas que necesitamos definir son un
  ejemplo exacto de lo que se puede hacer con schematic\_goal.
\end{framed}
